---
title: New season, new film
author: Regina Manansala
date: '2022-06-19'
slug: []
categories:
  - photos
tags:
  - film
  - photos
  - life
subtitle: ''
excerpt: 'A 30-day challenge that turn into almost 60 days and counting...'
layout: single
# links:
#   - icon: door-open
#     icon_pack: fas
#     name: website
#     url: /
---
Another photo challenge, this time using Lomography Metropolis film. We followed prompts from this <a href = "https://www.chantillysongs.com/2020/01/do-30-day-photo-challenge-for-new-year.html">photo challenge</a>. Here are my fav 15 with descriptions below. 

I honestly had no idea what to expect with this film and now I know not to use it during sunny days because some of my pictures outdoors just look overexposed. Some of the photos are still in another yet-to-be-completed-and-developed Portra 400 roll. The photos in the Portra 400 might end up better that some of these so I will probably post another update when that's developed and scanned.

```{r, echo = FALSE}
library(pixture)

paths <- list.files(".", pattern = ".JPG|.jpg", full.names = TRUE)
```

```{r line1, echo = FALSE}
pixgallery(paths[1:3],
           caption=c(
             "02 - Someone you love",
             "03 - Your favorite place",
             "04 - What makes you happiest"
             )
           )
```

Someone you love: <i>pretty self-explanatory</i>
<br>Your favorite place: <i>Antwerp is probably one of the best cities I've lived in and what else is more representative of Antwerp than its famous train station?</i>
<br>What makes you happiest: <i>I love being outdoors and people watching. Bonus points if it's at a market.</i>

```{r line2, echo = FALSE}
pixgallery(paths[4:6],
           caption=c(
             "05 - A beverage",
             "06 - Mornings",
             "07 - Evenings"
             )
           )
```

A beverage: <i>A beer from Cafe Ernest. This is when I learned that my little point-and-shoot is not the best camera for food pics. Funny story - I got the stomach flu that night. Not fun.</i>
<br>Mornings: <i>Arriving in Brussels for a day trip.</i>
<br>Evenings: <i>An evening by the Vismarkt in Brussels.</i>

```{r line3, echo = FALSE}
pixgallery(paths[7:9],
           caption=c(
             "08 - Nature",
             "11 - What you ate",
             "14 - Something funny"
             )
           )
```

Nature: <i>A cute cottage during our anniversary hike around Villers-la-Ville.</i>
<br>What you ate: <i>Apo's - one of our favorite places in Antwerp.</i>
<br>Something funny: <i>A sticker by our table at Cafe Ernest.</i>

```{r line4, echo = FALSE}
pixgallery(paths[10:12],
           caption=c(
             "15 - What's to my right",
             "16 - Now Playing",
             "18 - What I can't wait to do"
             # "19 - In motion",
             # "23 - Made me smile",
             # "28 - Something shiny"
             )
           )
```

What's to my right: <i>A fun view while waiting at the corner of Mechelsesteenweg and Britselei in Antwerp.</i>
<br>Now Playing: <i>Picked up a great Japanese funk record from Sugar Pie Records in Antwerp.</i>
<br>What I can't wait to do: <i>I can't wait to travel. I've been stuck in Belgium since December and I'm counting down the days until I get my residence card.</i>

```{r line5, echo = FALSE}
pixgallery(paths[13:15],
           caption=c(
             "19 - In motion",
             "23 - Made me smile",
             "28 - Something shiny"
             )
           )
```

In motion: <i>An installation at the Extra City Kunsthal.</i>
<br>Made me smile: <i>Cows!</i>
<br>Something shiny: <i>The Gilded buildings in Brussels' Grote Markt. The gold doesn't really shine through with this film, sadly.</i>